Dobbs' Decision And Abortion

### 2025-01-06 ProjectBlog/others/Natality/natality.qmd
abortion policy
natality data

As the paralle trend assumption is hard to satisfy in this study, I made a synthetic Texas with states with abortion free policies to examine the effects of the two policies on abortions.

>>>>

## Methodology

### Data

County by month level natality observations.

### Model

As the parall trend assumption is hard to satisfy in this study, I made a synthetic Texas with states (e.g., New York and California) with abortion free policies and take it as control group. I use a synthetic difference-in-difference estimator to examine the effects of the two policies on abortions.

## Results

My preliminary anticipation is that Dobbs' decision make one third of women that would chose to terminate pregnancy change their mind to give birth to a baby.
